% cv.tex
%%
%% This is my resumé, my curriculum vitae, my skill list.
%%
%% Originally based on Russel Dsouza's CV, pulled from
%% https://github.com/rshwndsz/cv/blob/main/CV.tex on 2022-05-03 and imported
%% here.

% Preamble
%% CVs should be one-sided, small-fonted, and on standard paper (I live in the
%% USA, so letter is standard).
\documentclass[letterpaper, 10pt, oneside]{article}
%% For HTML support
\usepackage[utf8]{inputenc}
%% Control Spacing between lines.
\usepackage{lwarp}
%% UTF-8 is the /minimum/ I use in terms of encoding depth.
\usepackage{setspace}
%% Use Table Extensions.
\usepackage{tabularx}
%% Allow Multi-Page tables.
\usepackage{longtable}
%% I prefer the HTML color model, as that is how I think of colors.
\usepackage[HTML]{xcolor}
%% For Hyperlink support.
\usepackage{hyperref}
%% For better link colors
\definecolor{color-link}{HTML}{462700}
\definecolor{color-file}{HTML}{004627}
\definecolor{color-url}{HTML}{462700}
\hypersetup{colorlinks  = true,
            linkcolor   = color-link,
            filecolor   = color-file,
            urlcolor    = color-url, 
            pdftitle    = {Cody's CV},
            pdfpagemode = FullScreen,
}
%% For nicer table support and thicker borders.
\usepackage{booktabs}
%% Setting up how page margins look.
\usepackage[left=.64in, right=.64in, bottom=.64in, top=.64in]{geometry}
%% For a thick underline - https://tex.stackexchange.com/a/443445 - unchanged
%% from Russel's CV.
\usepackage{lipsum}
%% For list customizations.
\usepackage{enumitem}

% === Setup ===
% Page numbers - 
% {arabic}=Arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{arabic}


% === My Commands ===
% Section title - Uppercase with first letter slightly bigger
\newcommand{\stitle}[1]{\normalsize{\textsc{#1}}}
% Bold & Italic
\newcommand{\bdit}[1]{{\textbf{#1}}}
% Use hyphens instead of bullets for lists
\def\labelitemi{--}
\begin{document}


% My name
\noindent\section*{Cody Ryan Perri}
\rule{\textwidth}{0.5ex}


\noindent \begin{longtable}{@{} p{0.13\linewidth} p{0.8\linewidth}}
  % Address & socials
  \stitle{Contact}     & 177 Oakville Dr APT TA
  \hfill \href{mailto:codyperri2@yahoo.com}{codyperri2@yahoo.com} \\
  
  \stitle{Information} & Pittsburgh, PA 15220
  \hfill \url{https://linkedin.com/in/codyperri2} \\
  
  & USA \hfill \textcolor{color-url}{+1 (724)-900-3860} \\ \\

  % Objective
  \stitle{Objective} & Logistician seeks full-time position with established shipping company in the Pittsburgh area.\\ \\
  
  % Research interests
  \stitle{Professional} & Logistics, Reporting, Project Planning and Management \\
  \stitle{Interests}   & Especially Involving Applied Mathematics \\ \\

  % Education
  \stitle{Education}
  
  & \textbf{\href{https://www.snhu.edu/}{Southern New Hampshire University}}
  \hfill \textsl{4.0} \\[-1.25em] & Bachelor of Applied Mathematics
  \hfill \hspace{-3em} \textsl{2022\ --\ Present} \\

  \\[-1.8ex]

  & \textbf{\href{https://www.kent.edu/}{Kent State University}}
  \hfill \textsl{3.25} \\
  & General Studies (no major)
  \hfill \hspace{-3em} \textsl{2014\ --\ 2015} \\

  \\[-1.8ex]

  & \textbf{\href{https://www.northallegheny.org/}{North Allegheny Senior High School}}
  \hfill \textsl{General} \\
  & High School Diploma
  \hfill \hspace{-3em} \textsl{2010\ --\ 2014} \\ \\

  % Work Experience
  & \bdit{Assistant Manager}
  \hfill  \\
  & \textsl{\href{https://www.aboutamazon.com/}{Amazon.com, LLC}}
  \hfill \textsl{Aug 2018\ --\ Sep 2022} \\
  
  & \parbox{0.8\textwidth}{I covered changing roles on the overnight sort
    shift including shift planning, monitoring and managing associate
    performance, and quality assurance. In Spring 2020, I took ownership of
    COVID-19 rollouts including training associates in temperature screening
    procedures, adjusting the building layout to meet social distancing
    guidelines, and consistently working with others to ensure up to date
    signage was posted site-wide. In September 2020, I transferred buildings
    to assist with the launch of the region’s newest delivery station. I
    started on the load out shift: my responsibilities included ensuring
    routes were scheduled for the correct times and monitoring route
    progress. In addition to my previous COVID-19 responsibilities, I handled
    preparing and overseeing testing—including the shipment of completed
    tests. In July 2021, I began overseeing the overnight shift in addition
    to the load out shift, where my responsibilities reflected a combination
    of both shifts.}
  \\
  \\
  & \bdit{Caterer}
  \hfill  \\
  & \textsl{\href{https://www.johnmarshallcatering.com/}{John Marshall Catering}}
  \hfill \textsl{Jan 2015\ --\ Dec 2018} \\
  
  & \parbox{0.8\textwidth}{}
  \\
  \\
  & \bdit{Delivery Driver/Dishwasher}
  \hfill  \\
  & \textsl{\href{https://www.totinsdiner.org/}{Totin's Diner}}
  \hfill \textsl{Oct 2012\ --\ Sep 2018} \\
  
  & \parbox{0.8\textwidth}{}
  \\
  \\
  \newpage
  % 
  \stitle{Relevant} & \bdit{Leadership}
  \hfill   \textsl{Team Building, Project Management, and Professional Development} \\
  \stitle{Skills} & \\[-1.75em]
  & \parbox{0.8\textwidth}{\begin{itemize}
    \item{\textsl{Team Building:} Basics of LEAN/6\sigma; Coaching and feedback to
        and from coworkers; Commitment to earning trust of those I lead;
        Adapting roles of a team to constantly changing environments;
        Achieving success when under stress by doing our best; Active
        listening and responding to the views of others.}
    \item{\textsl{Project Management:} Implementing projects related to
        COVID-19; Successfully ushering projects from conception to
        completion; Adapting to changing customer requests; Achieving more
        with less.}
    \item{\textsl{Professional Development:} Training associates in a variety
        of pathways; Clearly communicating standard operating procedures;
        Helping others develop themselves; Facilitating job rotation and
        remedial training for associates as needed.}
    \end{itemize}}
  \\
  \\
  & \bdit{Analytics}
  \hfill  \\
  & \textsl{}
  \hfill \textsl{Deep Diving Data, Problem Solving, and Applied Mathematics} \\
  
  & \parbox{0.8\textwidth}{\begin{itemize}
    \item{\textsl{Deep Diving Data:} Efficiently correlating data to show
        trends and root causes; Using Microsoft Excel to express and analyze
        data over time; Insisting on the highest standard of investigation to
        ensure solutions are effective.}
    \item{\textsl{Problem Solving:} Using the "5 Whys" to ensure the
        problem being solved is actually the problem at hand; Ensuring all
        voices are heard when gathering information; Taking an open-minded
        approach to each issue, making sure each solution is also a lesson
        learned for my team.}
    \item{\textsl{Applied Mathematics:} Learning constantly while pursuing
        Bachelor's Degree in Applied Mathematics; Finding new ways to utilize
        educational background in the professional sphere; Cultivating a deep
        desire to learn and improve myself each day.}
    \end{itemize}}
  \\
  \\
  \stitle{Relevant} & \bdit{Problem Solving}
  \hfill   \textsl{Achieving Success in Changing Environments} \\
  \stitle{Interests} & \\[-1.75em]
  & \parbox{0.8\textwidth}{\begin{itemize}
      
    \item{\textsl{Mathematical Background:} I enjoy finding patterns in data
        and trends over time. I want to eventually transition to a position
        in the applied mathematics field. I am not intimidated by large or
        complicated data sets.}
    \item{\textsl{Logistics:} I enjoy the process of ensuring efficient
        delivery of goods. I am deeply familiar with the different roles a
        delivery station takes through that process. I am passionate about
        the customer experience and delivering on the customer promise.}
    \item{\textsl{Varied Working Environment:} I do best in roles where the
        work changes from day to day, and my team and I need to adapt in a
        fast-paced environment. I enjoy leading a team to success even when
        things get difficult, and improving myself and my team over time. I
        love the opportunity to tackle a problem I have yet to attempt to
        solve.}
    \end{itemize}}
  \\
  \\
  \stitle{References} & \bdit{Professional / Personal}
  \hfill  \\
  & Available on Request.
\end{longtable}
\vspace*{\fill}
\begin{center}
  \tiny Made with Lua\LaTeX using GNU Emacs and Git, on GNU Guix 1.3.0.
\end{center}

\end{document}
